---
title: "first_hit"
author: "SKK"
date: "2023-12-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#load packages
```{r}
install.packages("pacman")
pacman::p_load(tidyverse, rlang, tidymodels, gridExtra, brms, cmdstanr, loo)
install.packages("naivebayes")
library(naivebayes)

setwd('.')
```

# load data
```{r}
fh_df <- read.csv("FIRST_VISIT.csv")
fh_df <- fh_df %>% 
  rename(First_hit=First_visit) %>% 
  rename(Trial=Trial_index) %>% 
  rename(Participant=ID)

fh_df$Task <- as.factor(fh_df$Task)#levels 
fh_df$Task  <- as.numeric(fh_df$Task)#assigning the level by overwriting the id.
fh_df$Task  <- as.factor(fh_df$Task)

fh_df$AOI <- as.factor(fh_df$AOI)#levels 
fh_df$AOI <- as.numeric(fh_df$AOI)#assigning the level by overwriting the id.
fh_df$AOI  <- as.factor(fh_df$AOI)


#classificaion problem
first <- fh_df %>% 
  filter(First_hit==1)
first <- subset(first,select=c("Participant","Task","AOI"))
#softmax
```

# define models
```{r}
model <- bf(AOI ~ Task) 
```

# get priors
```{r}
get_prior(
  model,
 first,
 family = categorical(link = "logit")
 )
```

```{r}
priors <- c(
  prior(normal(0, 1), class = "b", dpar = "mu2"),
  prior(normal(0, 1), class = "b", dpar = "mu3")
)
```

# Run model with priors
```{r warning=FALSE}
m_prior <-
  brm(
    model,
    data = first,
    prior = priors,
    family = categorical(link = "logit"),
    sample_prior="only",
    backend = "cmdstanr",
    file = "model_prior",
    warmup = 1000,
    iter = 4000,
    chains = 2,
    cores = 4,
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20
    )
  )
```

```{r warning=FALSE}
m_po <-
  brm(
    model,
    data = first,
    prior = priors,
    family = categorical(link = "logit"),
    backend = "cmdstanr",
    file = "m_pos",
    warmup = 1000,
    iter = 4000,
    chains = 2,
    cores = 4,
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20
    )
  )
```
```{r}
pop <- pp_check(m_po, ndraws = 100) + labs(title = "Posterior distribution") + xlim(-0.5,1.5)
pop
```


### Checking on the priors
```{r}

prp_m4 <- pp_check(fh_m4_prior, ndraws = 100) + labs(title = "Model 4 - prior") + xlim(-0.5, 1.5)
prp_m4


ggsave("prior_first_hit.jpg", prp_m4)

```

# Posterior



```{r}
variables(m_po) #check which names for the pp-update plots
 ```


### Prior Posterior Update Checks for model 4
```{r}
draw_m4 <- as_draws_df(fh_m4_pos)

#Plot the prior-posterior update plot for b:
pp4_int <- ggplot(draw_m4) +
  geom_density(aes(prior_Intercept), fill="steelblue", color="black",alpha=0.6) +
  geom_density(aes(b_Intercept), fill="#FC4E07", color="black",alpha=0.6) + 
  xlab('Intercept') +
  labs(title="Model 4 - Intercept") +
  theme_bw()

#Plot the prior-posterior update plot for the Task (b):
pp_m4_task <- ggplot(draw_m4) +
  geom_density(aes(prior_b_Task2), fill="steelblue", color="black",alpha=0.6) +
  geom_density(aes(b_Task2), fill="#FC4E07", color="black",alpha=0.6) + 
  xlab('Recognition') +
  labs(title="Model 4 - Recognition") +
  theme_bw()
  
#Plot the prior-posterior update plot for the AOI (b):
pp_m4_aoilegs <- ggplot(draw_m4) +
  geom_density(aes(`prior_b_AOIlegs`), fill="steelblue", color="black",alpha=0.6) +
  geom_density(aes(`b_AOIlegs`), fill="#FC4E07", color="black",alpha=0.6) + 
  xlab('b') +
  labs(title="Model 1 - AOI torso") +
  theme_bw()

#Plot the prior-posterior update plot for the AOI (b):
pp_m4_aoitorso <- ggplot(draw_m4) +
  geom_density(aes(`prior_b_AOItorso`), fill="steelblue", color="black",alpha=0.6) +
  geom_density(aes(`b_AOItorso`), fill="#FC4E07", color="black",alpha=0.6) + 
  xlab('b') +
  labs(title="Model 1 - AOI torso") +
  theme_bw()

#Plot the prior-posterior update plot for the interaction of the torso AOI and the Task:
pp_m4_taskaoi_torso <- ggplot(draw_m4) +
  geom_density(aes(`prior_b_Task:AOItorso`), fill="steelblue", color="black",alpha=0.6) +
  geom_density(aes(`b_Task:AOItorso`), fill="#FC4E07", color="black",alpha=0.6) + 
  xlab('b') +
  labs(title="Model 1 - interaction torso aoi and task") +
  theme_bw()

#Plot the prior-posterior update plot for the interaction of legs AOI and the task:
pp_m4_taskaoi_legs <- ggplot(draw_m4) +
  geom_density(aes(`prior_b_Task:AOIlegs`), fill="steelblue", color="black",alpha=0.6) +
  geom_density(aes(`b_Task:AOIlegs`), fill="#FC4E07", color="black",alpha=0.6) + 
  xlab('b') +
  labs(title="Model 1 - interaction legs aoi and task") +
  theme_bw()



#Plot the prior-posterior update plot for the correlation between varying intercepts and slopes:
pp_4_cor <- ggplot(draw_m4) +
  geom_density(aes(prior_cor_Participant), fill="steelblue", color="black",alpha=0.6) +
  geom_density(aes(cor_Participant__Task__AOIhead), fill="#FC4E07", color="black",alpha=0.6) + 
  geom_density(aes(cor_Participant__Task__AOItorso), fill="red", color="black",alpha=0.6) + 
  geom_density(aes(cor_Participant__Task__AOIlegs), fill="blue", color="black",alpha=0.6) + 
  geom_density(aes(cor_Participant__AOIhead__AOIlegs), fill="green", color="black",alpha=0.6) + 
  geom_density(aes(cor_Participant__AOIhead__AOItorso), fill="yellow", color="black",alpha=0.6) +
  geom_density(aes(cor_Participant__AOIlegs__AOItorso), fill="purple", color="black",alpha=0.6) +
  xlab('cor') +
  labs(title="Model 1 - correlation between varying intercepts and slopes") +
  theme_bw()


pp_4_sd_pi <- ggplot(draw_m4) +
  geom_density(aes(prior_sd_Participant__Intercept), fill="#FC4E07", color="black",alpha=0.3) +
  geom_density(aes(sd_Participant__Intercept), fill="#228B22", color="black",alpha=0.4) + 
  xlab('sd') +
  labs(title="Model 4 - Participant intercept sd") +
  xlim(-0.5, 1) +
  theme_bw()

pp_4_sd_paoi <- ggplot(draw_m4) +
  geom_density(aes(prior_sd_Participant__AOIlegs), fill="aquamarine", color="black",alpha=0.3) +
  geom_density(aes(prior_sd_Participant__AOItorso), fill="steelblue4", color="black",alpha=0.3) +
  geom_density(aes(sd_Participant__AOItorso), fill="steelblue", color="black",alpha=0.6) +
  geom_density(aes(sd_Participant__AOIlegs), fill="aquamarine4", color="black",alpha=0.6) +
    xlab('sd') +
  labs(title="Model 4 - Participant intercept sd") +
  xlim(-0.5, 1) +
  theme_bw()
  
pp_4_sd_ptaaoi <- ggplot(draw_m4) +
  geom_density(aes(`prior_sd_Participant__Task:AOIlegs`), fill="brown4", color="black",alpha=0.3) +
  geom_density(aes(`prior_sd_Participant__Task:AOItorso`), fill="grey", color="black",alpha=0.3) +
  geom_density(aes(`sd_Participant__Task:AOItorso`), fill="grey3", color="black",alpha=0.3) +
  geom_density(aes(`sd_Participant__Task:AOIlegs`), fill="brown3", color="black",alpha=0.3) +
    xlab('sd') +
  labs(title="Model 4 - Participant intercept sd") +
  xlim(-0.5, 1) +
  theme_bw()

pp_4_sd_pta <- ggplot(draw_m4) +
  geom_density(aes(prior_sd_Participant__Task), fill="aquamarine1", color="black",alpha=0.3) +
  geom_density(aes(sd_Participant__Task), fill="aquamarine4", color="black",alpha=0.3) +
    xlab('sd') +
  labs(title="Model 4 - Participant intercept sd") +
  xlim(-0.5, 1) +
  theme_bw()
  
  
pp_4_sd_ptri <- ggplot(draw_m4) +
  geom_density(aes(prior_sd_Trial), fill="grey", color="black",alpha=0.3) +
  geom_density(aes(sd_Trial__Intercept), fill="grey4", color="black",alpha=0.3) +
    xlab('sd') +
  labs(title="Model 4 - Participant intercept sd") +
  xlim(-0.5, 1) +
  theme_bw()
```

```{r}
summary(m_po)
#to look at r_hat, bulk and tail values
```
### Hypothesis testing:
```{r}
#general hypothesis
hypothesis(m_po, "mu2_Task3<mu2_Task2") 
#individual subjects
hypothesis(MLU_3, "Visit<0.03", group = "ID", scope="coef")
```

## Look at distributions, for example at credible intervals etc.

# Softmax
## load data
```{r}

```
## load packages
```{r}
library(rethinking)
```
## try with real data
```{r}
# Assuming df is your data frame
first$Task <- as.factor(first$Task)
first$AOI <- as.factor(first$AOI)

first$Task <- as.integer(first$Task)
first$AOI <- as.integer(first$AOI)

# Check the levels and make sure they start from 1
levels(as.factor(first$AOI))

```
```{r}
codem <- "
data {
  int N;         // Number of observations
  int K;         // Number of categories (aois)
  int aoi[N];    // Outcome
  int task[N];   // Task variable
}
parameters {
  matrix[N, K-1] a;    // Intercepts for each observation and category
  vector<lower=0>[N] b; // Association of task with first visit aoi for each observation
}
model {
  matrix[N, K] s;

  for (i in 1:N) {
    a[i] ~ normal(0, 1);
  }
  
  b ~ normal(0, 0.5);

 for (i in 1:N) {
    s[i, 1:K-1] = a[i,];
    s[i, K] = 0; // pivot
    aoi[i] ~ categorical(softmax(s[i, 1:K]'));
  }
} 
"
```

```{r}
dat_list <- list(
  N = nrow(first),
  K = length(unique(first$AOI)),
  aoi = first$AOI,
  task = first$Task
)

# Fit the model
m11.13 <- stan(model_code = codem, data = dat_list, chains = 4)

precis( m11.13 , 2 )

```




## try out model
```{r}
second <- first
second$AOI <- as.factor(second$AOI)
second$AOI <- as.numeric(second$AOI)
second$AOI <- as.factor(second$AOI)

second$Task <- as.factor(second$Task)
second$Task<- as.numeric(second$Task)
second$Task<- as.factor(second$Task)

third <- third %>%
  group_by(Participant) %>% 
  mutate(n=row_number()) %>% 
  mutate(Task=as.integer(Task)) %>% 
  mutate(Index=Task*1000+n)

fry <- xtabs(~AOI,second)
total_hits <- sum(fry) 

third <- third %>% 
  group_by(AOI) %>% 
  mutate(score=n()/total_hits) #change of each aoi with no restriction to task or any thing else

```

```{r}
N=nrow(second)
task=as.vector(as.integer(second$Index))

fry <- xtabs(~AOI,second)
total_hits <- sum(fry) 
score <- third$score #change of each aoi with no restriction to task or any thing else
p <- softmax(score)
```

```{r}
codem <- "
data{
  int N; //number of participants
  int K; // number of aoi's
  int aoi[N]; //outcome
  vector[K] task;
}
parameters{
  vector[K-1] a; //Intercepts for each participant, task, and category
  real<lower=0> b; //Association of task with first visit aoi for each participant
}

model{
  vector[N, K] p;
  vector[N, K] s;
  a ~ normal(0,1); //change??
  b ~ normal(0,0.5); //change??
  for (i in 1:N){
    for (j in 1:K){
    s[i,j]=a[i,j]+b[i]*task[i]
    }
    s[i,K] = 0; // pivot
    p[i,] = softmax( s[i,] );

  }

  aoi ~ categorical( p );
}

"
```


```{r}
dat_list <- list( N= nrow(second),
                  K=3 ,
                  aoi = as.vector(as.integer(second$AOI)),
                  task=as.vector(as.integer(second$Task))
)
m11.13 <- stan( model_code=codem , data=dat_list , chains=4 )
precis( m11.13 , 2 )

```

```{r}
post <- extract.samples(m11.13)
# set up logit scores
s1 <- with( post , a[,1] + b*task[1] )
s2_orig <- with( post , a[,2] + b*task[2] )
s2_new <- with( post , a[,2] + b*task[2]*2 )
# compute probabilities for original and counterfactual
p_orig <- sapply( 1:length(post$b) , function(i)
softmax( c(s1[i],s2_orig[i],0) ) )
p_new <- sapply( 1:length(post$b) , function(i)
softmax( c(s1[i],s2_new[i],0) ) )
# summarize
p_diff <- p_new[2,] - p_orig[2,]
precis( p_diff )

```


# fix dwell proportion
```{r}
df <- read.csv("DWELL_PROPORTION.csv")
#summerize aoi duration per trial
try <- df %>% 
  group_by(ID,Task,Trial_index,AOI_hit) %>% 
  mutate(AOI_duration=sum(Fixation.Duration))

df_filtered <- try %>%
  group_by(ID, Task, Trial_index, AOI_hit) %>%
  summarise(
    Dwell_TRIAL = first(Dwell_TRIAL),  # Keep the first value of dwell_trial
    AOI_duration = first(AOI_duration)  # Keep the first value of aoi_duration
  ) %>%
  distinct(AOI_hit, .keep_all = TRUE)

df_filtered <- df_filtered %>% 
  mutate(Dwell_pro=AOI_duration/Dwell_TRIAL)

#transform
df_filtered <- df_filtered %>% 
  mutate(t_aoi_pro=((Dwell_pro*(Dwell_TRIAL-1)+0.5)/Dwell_TRIAL))
```

# fix ID in dataframes
```{r}
df <- read.csv("fixations_MAGNIFISO.csv")
df$ID <- as.factor(df$ID)
df$ID <- as.numeric(df$ID)
df$ID <- as.factor(df$ID)
write.csv(df,"fixations_MAGNIFISO.csv")
```

```{r}
df <- df %>% 
  rename(AOI=AOI_hit)
result <- df %>%
  group_by(ID, Task, Trial_index) %>%
  mutate(first_row = row_number() == 1,
         change_in_AOI = AOI != lag(AOI, default = first(AOI))) %>%
  filter(first_row | change_in_AOI) %>%
  select(-first_row, -change_in_AOI)

# Print or view the result
print(result)

res <- result %>% 
  group_by(ID, Task, Trial_index) %>%
  filter(row_number() == 2) %>%
  ungroup()

second <- subset(res,select=c("ID","Task","Trial_index","AOI"))
second$AOI <- gsub("\\+", "", second$AOI)
second$ID <- as.factor(second$ID)
second$AOI <- as.factor(second$AOI)
second$Task <- as.factor(second$Task)
```


# Third try with soft max
```{r}
# Load necessary packages
library(rethinking)

# Define the Stan model
codem <- "
data {
  int N;         // Number of observations
  int K;         // Number of categories (AOIs)
  int aoi[N];    // Outcome
  int task[N];   // Task variable
}
parameters {
  matrix[N, K-1] a;    // Intercepts for each observation and category
  vector<lower=0>[N] b; // Association of task with the first visit AOI for each observation
}
model {
  matrix[N, K] p;
  matrix[N, K] s;

  for (i in 1:N) {
    a[i] ~ normal(0, 1);
  }
  
  b ~ normal(0, 0.5);

  for (i in 1:N) {
    for (j in 1:K) {
      s[i, j] = a[i, j] + b[i] * task[i];
    }
    s[i, K] = 0; // pivot
    aoi[i] ~ categorical(softmax(s[i, 1:K]'));
  }
}
"

# Specify the number of participants, categories, AOIs, and tasks
N <- 12739
K <- 3

# Create dummy data for illustration
set.seed(42)
aoi <- first$AOI
task <- first$Task

# Create data list
dat_list <- list(N = N, K = K, aoi = aoi, task = task)


# Compile the Stan model
model <- stan(model_code = codem,data=dat_list,chains=4, iter=1000)
```

```{r}

# Fit the model to the data
fit <- sampling(model)

```

Step 3: Extract Coefficients
```{r}
# Extract coefficients from the posterior samples
posterior_samples <- extract.samples(fit)

# Examine coefficients associated with the Task variable
coef_b <- colMeans(posterior_samples$b)
print(coef_b)

```

Here, coef_b contains the mean estimates for each coefficient associated with the Task variable.

Step 4: Interpretation
Interpret the coefficients in coef_b. Positive coefficients suggest an increase in the log-odds of choosing the first visit AOI as the Task variable increases, while negative coefficients suggest a decrease.

Step 5: Predictions
```{r}
# Create a data frame with all combinations of AOI and Task
new_data <- expand.grid(Task = 1:3, AOI = 1:K)

# Predict probabilities for each combination
predicted_probs <- predict(fit, newdata = new_data, draws = posterior_samples)
print(predicted_probs)
```

This will give you the predicted probabilities for each combination of AOI and Task based on the model.

Step 6: Visualization or Comparison
Visualize the predicted probabilities or compare them to draw conclusions about the influence of Task on AOI.

Please adjust the steps based on your specific data and research question. Let me know if you have any questions or if you'd like further clarification on any step!

# Multinomial logistic regression
```{r}
# Assuming df is your data frame
first$Task <- as.factor(first$Task)
first$AOI <- as.factor(first$AOI)

first$Task <- as.integer(first$Task)
first$AOI <- as.integer(first$AOI)

first$Task <- as.factor(first$Task)
first$AOI <- as.factor(first$AOI)


# Check the levels and make sure they start from 1
levels(first$AOI)
levels(first$Task)

```
```{r}
library(caret)
index <- createDataPartition(first$AOI, p =.7, list=FALSE)
train <- first[index,]
test <- first[-index,]
```
```{r}
train$AOI <- relevel(train$AOI,ref="1")
```

```{r}
require(nnet)
multi <- multinom(AOI~Task, data=train)
summary(multi)
```
```{r}
exp(coef(multi))
```
```{r}
head(round(fitted(multi),3)) #head only shows the 6 first
```
```{r}
train$AOIpred <- predict(multi,newdata=train,"class")
tab <- table(train$AOI,train$AOIpred)
round((sum(diag(tab))/sum(tab))*100,2)
```
73% accuracy on train

```{r}
test$AOIpred <- predict(multi,newdata=test,"class")
tab <- table(test$AOI, test$AOIpred)
round((sum(diag(tab))/sum(tab))*100,2)
tab
```
73% accuracy, hvor den classificere alle andre AOI's forkert bortset fra torsoTail...

# tilbage til brms
```{r}
install.packages("brms", dependencies = TRUE)
install.packages("cmdstanr")
pacman::p_load(tidyverse)
install.packages("rstan")
library(brms)
# Assuming your data is in a data frame called 'gaze_data'
first$AOI <- as.integer(first$AOI)
first$Task <- as.integer(first$Task)
# Fit Bayesian ANOVA model
model.matrix(~AOI*Task, data = second)
model <- brm(AOI ~0+ Task, data = second,family=categorical())
intercept <- brm(AOI~Task,data=second,family=categorical())
second$AOI <- relevel(second$AOI,ref="2")
model2 <- brm(AOI ~0+ Task, data = second,family=categorical())
intercept2 <- brm(AOI~Task,data=second,family=categorical())
inter2 <- brm(AOI~0+Task+AOI+Task*AOI,data=second,family = categorical(),chains = 4, cores = 2, iter = 4000,warmup = 2000)


# Display summary of the Bayesian ANOVA model
try <- summary(bayesian_anova_model)
try1 <- summary(inter)

# Perform post-hoc analysis using posterior_samples
posterior_samples <- #posterior_Samples deprecated

# Visualize the results (posterior distribution)
plot(as_draws_df(bayesian_anova_model))

# Display credible intervals for post-hoc comparisons
summary(as_draws_rvars(bayesian_anova_model))
```

#making a plot for it
```{r}
coef_data <- data.frame(
  Effect = c("Legs_Movement", "Legs_Recog", "Legs_Aest", "Torso_Movement", "Torso_Recog", "Torso_Aest"),
  Estimate = c(try[["fixed"]][1][[1]]),
  Lower_CI = c(try[["fixed"]][3][[1]]),
  Upper_CI = c(try[["fixed"]][4][[1]]),
  Task = c("Movement", "Species", "Aesthetic", "Movement", "Species", "Aesthetic"),
  AOI = c("Legs", "Legs", "Legs", "TorsoTail", "TorsoTail", "TorsoTail")         
)

Collected <- subset(first,select=c(AOI,Task)) %>% 
  mutate(Hit="First")
se <- subset(second,select=c(AOI,Task)) %>% 
  mutate(Hit="second")
Collected <- rbind(Collected,se)

se <- first %>% 
  mutate(total=n()) %>% 
  group_by(Task,AOI) %>% 
  mutate(count=n()) %>% 
  mutate(per=count/total) %>% 
  distinct(AOI, .keep_all = TRUE) %>% 
  ungroup()

install.packages('extrafont')
library(extrafont)
font_import(pattern="Cambria")
loadfonts(device = "win")

AOI_colors <- c( 
                      "TorsoTail"= "#6E0955",
                      "HeadExtension"= "#009BBB",
                      "Legs"= "#7E5738"
                      )
se$AOI <- gsub("2", "Legs", se$AOI)
se$AOI <- gsub("1", "HeadExtension", se$AOI)
se$AOI <- gsub("3", "TorsoTail", se$AOI)
se$Task <- gsub("1", "Movement", se$Task)
se$Task <- gsub("2", "Species", se$Task)
se$Task <- gsub("3", "Aesthetic", se$Task)

ggplot(se, aes(x=, y=per, fill=AOI)) +
  geom_boxplot() +
      scale_fill_manual(values = AOI_colors) +
  facet_wrap(~Task)+
  labs(title="AOI distribution",fill="AOI",x="Task",y="Percentage")+
    theme(text=element_text(family="Cambria"))
ggsave("AOI_first_hit_distribution.png")

#boxplot
se1 <- second %>%
  group_by(Participant,Task) %>% 
  mutate(total=n()) %>% 
  group_by(Participant,Task,AOI) %>% 
  mutate(count=n()) %>% 
  mutate(per=count/total) %>% 
  distinct(AOI, .keep_all = TRUE) %>% 
  ungroup()

se1$AOI <- gsub("2", "Legs", se1$AOI)
se1$AOI <- gsub("1", "HeadExtension", se1$AOI)
se1$AOI <- gsub("3", "TorsoTail", se1$AOI)
se1$Task <- gsub("1", "Movement", se1$Task)
se1$Task <- gsub("2", "Species", se1$Task)
se1$Task <- gsub("3", "Aesthetic", se1$Task)

ggplot(se1) +
  aes(y="",x = Task, fill = AOI) + theme_minimal() +

  scale_fill_manual(values = AOI_colors) +
  geom_boxplot() +
  labs(title="AOI distribution",fill="AOI",x="Task",y="Proportion")+
  facet_wrap(vars(Task))+
  theme(text=element_text(family="Cambria"),axis.ticks.x=element_blank(),axis.text.x=element_blank())
ggsave("AOI_first_hit_boxplot.png",width = 7, height = 5, units = "in")
```


# til t.test
```{r}
options(mc.cores = parallel::detectCores())

# Step 4: Build the regression model
rstanarm::stan_glm(AOI ~ Task, data = first, family = categorical())
```

# naive bayes
```{r}
install.packages("naivebayes")
library(naivebayes)

mb <- multinomial_naive_bayes(x=second$AOI,y=second$Task,laplace = laplace)
```
```{r}
set.seed(121)
ind <- sample(2,nrow(second),replace=T,prob=c(0.8,0.2))
train <- second[ind==1,]
test <- second[ind==2,]

model <- naive_bayes(AOI ~ Task*AOI, data=train, usekernel=T)
plot(model)
```
```{r}
p <- predict(model,train,type='prob')
head(cbind(p,train))
summary(model)
```
```{r}
p1 <- predict(model,train)
tab1 <- table(p1,train$AOI)
tab1
sum(diag(tab1))/sum(tab1)
```
```{r}
p2 <- predict(model,test)
tab2 <- table(p2,test$AOI)
tab2
sum(diag(tab2))/sum(tab2)
```



#classifier
```{r}
# Create and train the Naive Bayes classifier
first$Task <- as.factor(first$Task)
first$AOI <- as.factor(first$AOI)

second$AOI <- gsub("2", "Legs", second$AOI)
second$AOI <- gsub("1", "HeadExtension", second$AOI)
second$AOI <- gsub("3", "TorsoTail", second$AOI)
second$Task <- gsub("1", "Movement", second$Task)
second$Task <- gsub("2", "Species", second$Task)
second$Task <- gsub("3", "Aesthetic", second$Task)

nb_classifier <- naive_bayes(AOI ~ Task, data = second)
nb <- naive_bayes(AOI ~ Task*AOI, data = second)
print(nb)
print(nb_classifier)
```


```{r}
# Display the summary of the model
print(nb_classifier)
```


```{r}
# Make predictions on new data (for example, using the same dataset for demonstration)
predictions <- predict(nb, newdata = second,type="class")
tab <- table(predictions,second$AOI)
tab
round((sum(diag(tab))/sum(tab))*100,2)

```
```{r}
prp <- predict(nb_classifier, newdata = second,type="prob")
table(prp,second$AOI)
```


```{r}
# Display the confusion matrix
table(predictions, first$AOI)
coef(nb)
```


# ONCE MORE
```{r}
library(brms)
df <- read.csv("C:/Users/sarak/OneDrive - Aarhus universitet/26102021/Cog sci/5_semester/Bachelor/bachelor - github/analysis/fixations_MAGNIFISO.csv") #starting over
d <- subset(df,select=c("ID","Task","Trial_index","Stimuli","AOI_hit","Fixation.Duration"))

second <- d %>% 
  group_by(ID,Task,Trial_index) %>% 
  slice(2)

second <- second %>% 
  rename(AOI=AOI_hit)

second$AOI <- gsub("\\+.*","",second$AOI)
second$Task <- gsub("style", "Aesthetic", second$Task)
second$Task <- gsub("act", "Movement", second$Task)
second$Task <- gsub("recog", "Species", second$Task)


second$first_visit <- 1
legs <- second
legs$first_visit <- 0
for (line in seq(1,nrow(legs))){
  if (legs$AOI[line]=="Head"){
    legs$AOI[line] <- "Legs"
  }else if (legs$AOI[line]=="Legs"){
    legs$AOI[line] <- "Torso"
  }else if (legs$AOI[line]=="Torso"){
    legs$AOI[line] <- "Head"
  }
}
head <- second
head$first_visit <- 0
for (line in seq(1,nrow(head))){
  if (head$AOI[line]=="Head"){
    head$AOI[line] <- "Torso"
  }else if (head$AOI[line]=="Legs"){
    head$AOI[line] <- "Head"
  }else if (head$AOI[line]=="Torso"){
    head$AOI[line] <- "Legs"
  }
}

s <- rbind(head,legs)
se <- rbind(second,s)
#the real stuff
se$Task <- as.factor(se$Task)
se$AOI <- as.factor(se$AOI)

formula <- first_visit ~ 0 + Task +Task:AOI

#3 has the head as reference, 4 legs, 5 torso
se$AOI <- relevel(se$AOI,ref="Head")

#find the priors
get_prior(formula = formula,data=se,family=bernoulli(link="logit"))
#set uninformative priors
ber_prior3 <- c(prior(normal(0,1),class="b",coef="TaskAesthetic"),
               prior(normal(0,1),class="b",coef="TaskMovement"),
               prior(normal(0,1),class="b",coef="TaskSpecies"),
               prior(normal(0,1),class="b",coef="TaskSpecies:AOILegs"),
               prior(normal(0,1),class="b",coef="TaskAesthetic:AOILegs"),
              prior(normal(0,1),class="b",coef="TaskSpecies:AOITorso"),
              prior(normal(0,1),class="b",coef="TaskAesthetic:AOITorso"),
              prior(normal(0,1),class="b",coef="TaskMovement:AOITorso"),
              prior(normal(0,1),class="b",coef="TaskMovement:AOILegs")
               )

#3 has the head as reference, 4 legs, 5 torso
se$AOI <- relevel(se$AOI,ref="Legs")

ber_prior4 <- c(prior(normal(0,1),class="b",coef="TaskMovement"),
               prior(normal(0,1),class="b",coef="TaskSpecies"),
               prior(normal(0,1),class="b",coef="TaskAesthetic"),
               prior(normal(0,1),class="b",coef="TaskSpecies:AOIHead"),
               prior(normal(0,1),class="b",coef="TaskAesthetic:AOIHead"),
              prior(normal(0,1),class="b",coef="TaskSpecies:AOITorso"),
              prior(normal(0,1),class="b",coef="TaskAesthetic:AOITorso"),
              prior(normal(0,1),class="b",coef="TaskMovement:AOITorso"),
              prior(normal(0,1),class="b",coef="TaskMovement:AOIHead")
               )
#3 has the head as reference, 4 legs, 5 torso
se$AOI <- relevel(se$AOI,ref="Torso")

ber_prior5 <- c(prior(normal(0,1),class="b",coef="TaskMovement"),
               prior(normal(0,1),class="b",coef="TaskSpecies"),
               prior(normal(0,1),class="b",coef="TaskAesthetic"),
               prior(normal(0,1),class="b",coef="TaskSpecies:AOIHead"),
               prior(normal(0,1),class="b",coef="TaskAesthetic:AOIHead"),
              prior(normal(0,1),class="b",coef="TaskSpecies:AOILegs"),
              prior(normal(0,1),class="b",coef="TaskAesthetic:AOILegs"),
              prior(normal(0,1),class="b",coef="TaskMovement:AOILegs"),
              prior(normal(0,1),class="b",coef="TaskMovement:AOIHead")
               )
#fit priors
head <- brm(formula = formula,  
                   data=se, 
                   prior = ber_prior3,
                   family = bernoulli(link = "logit"),
                   warmup = 500, 
                   iter = 2000, 
                   chains = 2, 
                   inits= "0",
           file = "prior_bullshit_3",
                   cores=2,
                   seed = 123)
#check 'em
pp_check(AAH,ndraws=100) #looks good

#fit posterior model
torso <- brm(formula = formula,  
                   data=se, 
                   prior = ber_prior5,
                  sample_prior = T, #THIS IS WHAT MAKES IT POSTERIOR
                   family = bernoulli(link = "logit"),
                   warmup = 2000, 
                   iter = 4000, 
                   chains = 2, 
                   inits= "0", 
          file = "posterior_bull_5",
                   cores=2,
                   seed = 123)
#check tha'
pp_check(AH,ndraws=100) #looks good

#get estimates
summary(AH)


#do hypothesis testing
#head
hypothesis(head,"TaskSpecies > (TaskMovement+TaskAesthetic)/2")
hypothesis(head,"TaskMovement:AOILegs > TaskMovement:AOITorso")
hypothesis(head,"TaskAesthetic:AOITorso = TaskAesthetic:AOILegs")
#legs
hypothesis(legs,"TaskMovement > (TaskSpecies+TaskAesthetic)/2")
hypothesis(legs,"TaskSpecies:AOIHead > TaskSpecies:AOITorso")
hypothesis(legs,"TaskAesthetic:AOIHead = TaskAesthetic:AOITorso")
#torso
hypothesis(torso,"TaskMovement:AOILegs > TaskMovement:AOIHead")
hypothesis(torso,"TaskSpecies:AOIHead > TaskSpecies:AOILegs")
hypothesis(torso,"TaskAesthetic:AOILegs = TaskAesthetic:AOIHead")

```

# boxplot
```{r}
se1 <- second %>%
  group_by(Trial_index,Task,AOI) %>% 
  mutate(count=n()) %>% 
  distinct(AOI, .keep_all = TRUE) %>% 
  ungroup()
se1$AOI <- gsub("TorsoTail", "Torso", se1$AOI)
se1$AOI <- gsub("HeadExtensions", "Head", se1$AOI)
se1$Task <- gsub("style", "Aesthetic", se1$Task)
se1$Task <- gsub("act", "Movement", se1$Task)
se1$Task <- gsub("recog", "Species", se1$Task)

p_fix <- ggplot(se1, aes(x = Task, y = count, fill = AOI)) +
  geom_boxplot() +
  ggtitle("First hit") +
  xlab("Task") +
  ylab("Proportion") +
  theme_bw() + 
  theme(text = element_text(family = "Cambria")) +
  scale_fill_manual(values=c(Head = "#009BBB", Legs = "#7E5738", Torso = "#6E0955")) +
  theme(text = element_text(size = 16), axis.text=element_text(size=12),
        plot.title=element_text(size=20,face="bold"))
p_fix <- p_fix + stat_summary(fun.y=mean,  geom="point", size=2,color="white", position = position_dodge(width = 0.75))
p_fix

ggsave("first_box.jpg", p_fix,  width = 10, height = 6, dpi = 300)
```

